Shades of Green

### 2023-09-25 docs/presentations/20230928-sehm_presentation.qmd
update bv trends fig in sehm_pres and figures.py

## Trends in Bioeconomy Visions{.smaller}
### [No Bioeconomy]{.text-gray-600}, [Bioecology]{style="color:#cc78bc;"}, [Bioresource]{style="color:#de8f05;"} and [Biotechnoloy]{style="color:#029e73;"}{.smaller}

@@

color_map = {
    "No Bioeconomy Vision": "rgb(0.8, 0.8, 0.8)",  # Gray
    "Bioecology Vision": "#cc78bc",  # Purple
    "Bioresource Vision": "#de8f05",  # Orange
    "Biotechnology Vision": "#029e73",  # Green
}

def plot_bv_trends_interactive(df):
    traces = []

    for bv, bioeconomy_vision in df.groupby("bioeconomy_vision"):
        traces.append(
            go.Scatter(
                x=bioeconomy_vision["year"],
                y=bioeconomy_vision["count"],
                name=bv,
                mode="lines",
                line=dict(color=color_map[bv]),  # Set line color based on the color_map
            )
        )

    fig = go.Figure(data=traces)
    fig.update_layout(showlegend=False, hovermode="x unified", height=550)
    fig.show()

plot_bv_trends_interactive(count_certain_bioeconomy_visions)

>>>>

## Trends in Bioeconomy Visions{.smaller}
### [No Vision]{.text-gray-600}, [Bioecology]{style="color:#cc78bc;"}, [Bioresource]{style="color:#de8f05;"} and [Biotechnoloy]{style="color:#029e73;"}{.smaller}

@@

plot_bv_trends_interactive(count_certain_bioeconomy_visions).show()
